Real-Time Activity Classification by Matched Filtering using Body-Worn Accelerometers

### 2016-09-24 notes/paper/paper.tex
Updates to the graphs

We chose this method for its simplicity and robustness against outliers in our training set. We anticipate that the user will have idle motion at the start and end of their training duration when they activate the training mode and with possible disruptions during the process.
%
\section{Performance and Throughput}
%
\subsection{Algorithm Performance}
%
The Kinetisense sensor was used for the algorithm performance analysis in this paper.
This unit has a three-axis accelerometer with an acceleration range of -5g to +5g and a sampling rate of 128Hz.
Samples of walking, jogging, and bicycling have been recorded with this unit and was attached to the ankle of the user.
A separate instance of walking data has been used specifically for training the classifier.
%
\begin{figure}[!ht]
  %\captionsetup[subfigure]{labelformat=empty}
  \centering
  \subfloat[\label{fig:frac_walking_jogging}]{\includegraphics[width=0.45\textwidth]{fraction_threshold_walking_to_jogging.png}}
  \quad
  \subfloat[\label{fig:frac_walking_bicycling}]{\includegraphics[width=0.45\textwidth]{fraction_threshold_walking_to_bicycling.png}}
  \centering
  \quad
  \subfloat[\label{fig:roc_walking_jogging}]{\includegraphics[width=.45\textwidth]{ROC_walk_to_run.png}}
  \centering
  \quad
  \subfloat[\label{fig:roc_walking_bicycling}]{\includegraphics[width=.45\textwidth]{ROC_walk_to_bike.png}}
  \caption{Matched-filter performance comparing jogging and bicycling data against a reference for walking. Results produced at decimation 8. Figures (c) and (d) are the corresponding ROC curves produced from (a) and (b) respectively.}
  \label{fig:MF_performance}
\end{figure}
%
Figures \ref{fig:frac_walking_jogging} and \ref{fig:frac_walking_bicycling} show the fraction of the correlation results that exceed the given correlation threshold when comparing the walking data reference to the given activity.
As we would expect, the walking data reference matches better to walking data than to the other activities. The tail in figure \ref{fig:frac_walking_jogging} is attributed to brief moments of walking that was recorded during the jogging data collection.
ROC curves were produced from these corresponding results in figures \ref{fig:roc_walking_jogging} and \ref{fig:roc_walking_bicycling} to illustrate the effectiveness of the matched-filter as a classifier.
Because the bicycling motions are considerably different from walking relative to jogging, we would expect better performance from our classifier for bicycling.
%
%\FloatBarrier
%
\subsection{Throughput Performance}
%
To assess the real-time processing potential of the algorithms outlined in this paper, a throughput assessment was performed on the MSP432P401R microcontroller with varying parameters.
The Texas Instruments - MSP432P401R is a low power plus performance microcontroller that is based on the ARM 32-Bit Cortex-M4F processor.
Some of the notable features of the MSP432P410R is having a clock frequency of 48 MHz, 64 kB SRAM, 256 kB Flash Memory, and has an IEEE 754-compliant single-precision Floating-Point Unit (FPU) and Memory Protection Unit (MPU).
The single-precision processing capability on this unit provides us with the dynamic range necessary to process the algorithms that fixed-point processing cannot provide.
The 64 kB of SRAM provides sufficient space to process the results found in figure \ref{fig:timing} and
the 256 kB is more than enough flash memory to store the program and data references.
The clock frequency operates at 48 MHz which drives the execution speed.

>>>>

We chose this method for its simplicity and robustness against outliers in our training set. We anticipate that the user will have idle motion at the start and end of their training duration when they activate the training mode and with possible disruptions during the process.
%
\section{Performance and Throughput}
%
\subsection{Algorithm Performance}
%
The Kinetisense sensor was used for the algorithm performance analysis in this paper.
This unit has a three-axis accelerometer with an acceleration range of -5g to +5g and a sampling rate of 128Hz.
Samples of walking, jogging, and bicycling have been recorded with this unit and was attached to the ankle of the user.
A separate instance of walking data has been used specifically for training the classifier.
%
\begin{figure}[!ht]
  %\captionsetup[subfigure]{labelformat=empty}
  \centering
  \subfloat[\label{fig:frac_walking_jogging}]{\includegraphics[width=0.45\textwidth]{fraction_threshold_walking_to_jogging.png}}
  \quad
  \centering
  \subfloat[\label{fig:frac_walking_bicycling}]{\includegraphics[width=0.45\textwidth]{fraction_threshold_walking_to_bicycling.png}}
  \centering
  \quad
  \subfloat[\label{fig:roc_walking_jogging}]{\includegraphics[width=0.45\textwidth]{ROC_walk_to_run.png}}
  \centering
  \quad
  \subfloat[\label{fig:roc_walking_bicycling}]{\includegraphics[width=0.45\textwidth]{ROC_walk_to_bike.png}}
  \caption{Matched-filter performance comparing jogging and bicycling data against a reference for walking. Results produced at decimation 8. Figures (c) and (d) are the corresponding ROC curves produced from (a) and (b) respectively.}
  \label{fig:MF_performance}
\end{figure}
%
Figures \ref{fig:frac_walking_jogging} and \ref{fig:frac_walking_bicycling} show the fraction of the correlation results that exceed the given correlation threshold when comparing the walking data reference to the given activity.
As we would expect, the walking data reference matches better to walking data than to the other activities. The tail in figure \ref{fig:frac_walking_jogging} is attributed to brief moments of walking that was recorded during the jogging data collection.
ROC curves were produced from these corresponding results in figures \ref{fig:roc_walking_jogging} and \ref{fig:roc_walking_bicycling} to illustrate the effectiveness of the matched-filter as a classifier.
Because the bicycling motions are considerably different from walking relative to jogging, we would expect better performance from our classifier for bicycling.
%
%\FloatBarrier
%
\subsection{Throughput Performance}
%
To assess the real-time processing potential of the algorithms outlined in this paper, a throughput assessment was performed on the MSP432P401R microcontroller with varying parameters.
The Texas Instruments - MSP432P401R is a low power plus performance microcontroller that is based on the ARM 32-Bit Cortex-M4F processor.
Some of the notable features of the MSP432P410R is having a clock frequency of 48 MHz, 64 kB SRAM, 256 kB Flash Memory, and has an IEEE 754-compliant single-precision Floating-Point Unit (FPU) and Memory Protection Unit (MPU).
The single-precision processing capability on this unit provides us with the dynamic range necessary to process the algorithms that fixed-point processing cannot provide.
The 64 kB of SRAM provides sufficient space to process the results found in figure \ref{fig:timing} and
the 256 kB is more than enough flash memory to store the program and data references.
The clock frequency operates at 48 MHz which drives the execution speed.
